### 2021-06-15 publications/2020-03-paper/revisions/review-responses.tex

% use the tnoteref command within \title for footnotes;
% use the tnotetext command for the associated footnote;
% use the fnref command within \author or \address for footnotes;
% use the fntext command for the associated footnote;
% use the corref command within \author for corresponding author footnotes;
% use the cortext command for the associated footnote;
% use the ead command for the email address,
% and the form \ead[url] for the home page:
%
% \title{Title\tnoteref{label1}}
% \tnotetext[label1]{}
% \author{Name\corref{cor1}\fnref{label2}}
% \ead{email address}
% \ead[url]{home page}
% \fntext[label2]{}
% \cortext[cor1]{}
% \address{Address\fnref{label3}}
% \fntext[label3]{}

\title{The role of current and emerging technologies in meeting Japan's mid- to long-term carbon reduction goals\\
\large Response to Review Comments}
\author{Anshuman Chaube, Andrew Chapman, Akari Minami, James Stubbins, Kathryn Huff}

% use optional labels to link authors explicitly to addresses:
% \author[label1,label2]{<author name>}
% \address[label1]{<address>}
% \address[label2]{<address>}

%\author[uiuc]{Kathryn Huff}
%        \ead{kdhuff@illinois.edu}
%  \address[uiuc]{Department of Nuclear, Plasma, and Radiological Engineering,
%        118 Talbot Laboratory, MC 234, Universicy of Illinois at
%        Urbana-Champaign, Urbana, IL 61801}
%
% \end{frontmatter}
\maketitle
\section*{Review General Response}
We would like to thank the reviewers for their detailed assessment of
this paper. Your suggestions, clarifications, and comments have resulted in 
changes which improved the paper.

@@

\begin{questions}
        \section*{Reviewer 1}

        %---------------------------------------------------------------------

         \question "The largest contribution to global greenhouse gas (GHG) emissions, some 73\%, comes from energy consumption in the transportation, electricity and heat, buildings, manufacturing, and construction sectors [2]."
Since the focus of the paper is on electricity, the share of GHG should be presented separately.

        \begin{solution}
                Thank you for these comments. We appreciate your detailed review. For the comment above, the following text has been added to the paper
        \end{solution}

         \question "Japan has been rapidly deploying renewables and has attempted to transition away from nuclear power since the Fukushima Daiichi accident [3]. Yet Japan is also considering reinvigorating its nuclear power sector, evidenced by the restart of its nuclear reactors [4]."
 away from nuclear energy is not true and contradicts itself directly in the following sentence

        \begin{solution}
                Thank you for these comments. For the comment above, the following text has been added to the paper to make the transition between the two statements less jarring. However, the narrative was fundamentally true for a while, as indicated by the /slow-restart of nuclear power plants and increasing reliance on coal, as shown by TEPCO(CHECK PUBLISHER NAME)'s Annual Electricity Review.

         \question "lessons learnt from these decarbonisation simulations could inform global energy policy by delineating potential transition pathways, identifying key novel technologies, and their most significant parameters."
	added value not clearly elaborated in comparison to existing literature        
        \begin{solution}
                Thank you for these comments. We appreciate your detailed review. For the comment above, the following text has been added to the paper
        \end{solution}

         \question "We account for the carbon cost of each technology using an emission coefficient that incorporates both direct emissions and life cycle emissions averaged over the entire operating lifetime for each technology"	
         Describe in more detail how calculations are made here. How do the factors enter the model? Statically? Separately for the production, use and disposal phases? Where does the data come from? CO2 only or CO2 equivalents?

        \begin{solution}
                Thank you for these comments.  For the comment above, the following text has been added to the paper
        \end{solution}

         \question "or hydrogen electrolysers and fuel cells, life-cycle emissions from just the stack are considered, as balance-of-plant emissions from utility scale hydrogen depend strongly on the type of plant and the source of energy used for electrolysis."
Does this mean that H2 goes in emission-free? Then this would have to be clearly stated.
        \begin{solution}
                Thank you for these comments. We appreciate your detailed review. For the comment above, the following text has been added to the paper
        \end{solution}

         \question Figure 1-5 starts at 2013, until when is historical data shown and when does simulation start?
        \begin{solution}
                Thank you for these comments. We appreciate your detailed review. For the comment above, the following text has been added to the paper
        \end{solution}

@@

                 Thank you for your comment. The same table is present in the draft at the end of Section 4.2. We have not placed the table at the beginning of the section for the sake of readability, specifically so that the reader may first be introduced to the concept and scope of our sensitivity analysis and the parameters therein, before diving into the detailed ranges of variation.

        \end{solution} 
                      %--------------------------------------------------------------------
                        \question   The Acknowledgement section mentions the funding source as the ministry of culture and others. What about the impact of suggested technologies on the culture and tradition of the country. Sustainable energy goals must meet social, economic, environmental and technological sustainability. Culture is an integral part of social sustainability of any energy resource.

        \begin{solution}

                 Thank you for your comment. We have simply referenced a source of funding. The focus of the paper is on modelling the electricity supply sector of a developed nation using TIMES while reducing carbon emissions. Cultural impacts are beyond the scope of our paper.

@@

        \end{solution} 
                              %--------------------------------------------------------------------
                        \question   Finally, I appreciate the authors for writing such a  thought provoking paper. I personally believe Nuclear Power is the only energy source which can provide sustainable energy for a long-time horizon like 2100. Starting from small energy sources such as nuclear battery to GW size generators, nuclear power has all in it. It would be great if the authors investigate the major impediments to a nuclear dominated energy scenario. Can the political and social constructs of the nation and for that matter the whole world accept nuclear power? Since Reliability theory says that all systems eventually fail, should not we give nuclear power a fair chance?

        \begin{solution}

                 Thank you for your comment. We appreciate the depth of your question. We have referenced nuclear-specific challenges throughout the paper in discussing the associated cost, the safety concerns especially after Fukushima-Daiichi, and the lack of public acceptance. However, the focus of the paper is on modelling the electricity supply sector using TIMES while reducing carbon emissions. Investigating impediments to any specific technology and proposing solutions to such impediments is beyond the scope of our paper, which aims to conduct an technologically-impartial analysis into decarbonisation transition scenarios.

        \section{Reviewer 3}

         \question Table 1. Please, remove the refrence from the table and include it in the table caption.
        \begin{solution}
                Thank you for these comments. We appreciate your detailed review. The requested changes have been made to Table 1, and the caption now reads

        \end{solution}  
                                      %--------------------------------------------------------------------

         \question Line 14 of page 15, please remove bold text.
        \begin{solution}
                Thank you for these comments. The requested text has been switched from bold to normal. To make similar text congruent with this change, all other transition costs have been changed from bold to normal.

        \end{solution}  
                                      %--------------------------------------------------------------------

\end{questions}
%\bibliographystyle{elsarticle-num}
%\bibliography{../2019-Scenarios}
\end{document}

### 2021-06-16 publications/2020-03-paper/revisions/review-responses.tex

        \begin{solution}
                Thank you for these comments. We appreciate your detailed review, which has certainly improved the paper. Regarding the parameters that must be considered, we have referenced the Paris Agreements which state the international considerations, and the Japanese Basic Energy Plan and the 3E+S approach, which we have summarised briefly in the introduction chapter. Since the focus of our paper is not on energy policy review and analysis, further details of these parameters are left in the references for the sake of brevity.
        \end{solution}

        %---------------------------------------------------------------------

        \question I have some apprehensions regarding the long-term horizon of 2100 for investigating the impact of the technologies. Such a long duration will involve many uncertainties. Further, the technology growth has been exponential in the last century. Therefore, it seems plausible that new technologies will be introduced in the energy mix. How the current paper deals with such uncertainties and technology disruptions?

        \begin{solution}
                 Thank you for your comment. We have conducted a thorough literature review to identify key technologies that could play a significant role in decarbonisation at scale. Likely changes in key technology parameters such as investment cost, emission coefficient etc. are incorporated dynamically through learning curves obtained from our references, and using TIMES interpolation features. Many of these data sources identify median values and ranges of key parameters in the original references. Beyond that, it is true that novel technologies may emerge in the future, and they will be incorporated in any future simulations that we conduct. The final paragraph of the Conclusion section has been revised to indicate the same :
                 ...as trucks and pipelines on hydrogen and CCS is also worth investigating. \textbf{Any new technologies that develop in the future and promise rapid decarbonisation should also be incorporated in such work.}

@@

        \end{solution}

                \question Carbon capture and sequestration is not a new technology. It has been utilized since long. Please highlight the chronological evolution of CCS and Hydrogen technologies to put your contributions in context. In fact, a table showing such chronological evolution for all the suggested technologies viz. nuclear power, wind, solar must be provided.

        \begin{solution}
                 Thank you for your comment. While carbon capture technology has been available in some form for a variety of applications since early 2000s, high-efficiency utility-scale carbon capture and sequestration plants have not been developed beyond the pilot stage in any nation, including Japan. This is further indicated by our data references provided by the EIA, which projects the first commercial prototype to become available in 2022-23 (see Table A.8). We have amended the initial reference to "carbon capture and sequestration" to "utility-scale carbon capture and sequestration" for further clarity.

### 2021-06-16 publications/2020-03-paper/introduction.tex
updates manuscript to latest version

\section{Introduction} \label{Introduction}
In order to mitigate climate change and to improve environmental outcomes, many nations are actively seeking to reduce carbon emissions, and have formalised this goal through the Paris Agreements \cite{united_nations_framework_convention_on_climate_change_unfccc_submission_2015}. The largest contribution to global \gls{GHG} emissions, some 73\%, comes largely from energy consumption in the transportation, electricity and heat, buildings, manufacturing, and construction sectors \cite{ge_4_2020}. Developed nations rich in natural resources can reduce \gls{GHG} emissions by switching to natural gas or implementing \gls{CCS} at fossil fuel plants. However, these options are often economically infeasible for developing nations, which will lead to increased emissions through greater coal use \cite{international_energy_agency_latest_2019}. Japan, a developed nation without fossil fuel resources, is likely to follow a different path to reduce emissions, evidenced by the restart of nuclear reactors and a shift towards large-scale renewable energy deployment \cite{international_energy_agency_latest_2019}.

Although influenced by the Paris Agreements, Japanese energy policy is governed by the Basic Energy Plan \cite{meti_japans_2018}, which outlines national policy towards a new energy system for the years 2030 and 2050 cognizant of limited indigenous resources, the impact of the Fukushima incident, and external pressures on energy supplies \cite{meti_annual_2018}. The plan reaffirms Japanese benchmarks for evaluating the energy system, first and foremost, within the context of energy security, followed by economic efficiency, safety, and the environment (summarised as `3E+S'; ibid). Although the Japanese 3E+S goals and the Paris Agreement targets have some parallels, the plan does not detail how the 2050 emission reduction target of 80\% is to be met. Matsuo et. al have suggested that electrification of a number of sectors will be required to achieve the ambitious 2050 target, underpinned by low-carbon technologies \cite{matsuo_quantitative_2018}. For the power sector to achieve such a target, near-zero emissions are required, and early action utilising existing technologies is preferable to delayed action utilising future technologies \cite{ashina_roadmap_2012}. The strategies currently under consideration include reinvigorating nuclear power, deploying \gls{CCS} to fossil fuel power plants, and ushering in a hydrogen economy based on renewable energy-based electrolysis as well as hydrogen imports from abroad \cite{ashina_roadmap_2012, matsuo_quantitative_2018, meti_basic_2017}.

>>>>

\section{Introduction} \label{Introduction}
In order to mitigate climate change and to improve environmental outcomes, many nations are actively seeking to reduce carbon emissions, and have formalised this goal through the Paris Agreements \cite{united_nations_framework_convention_on_climate_change_unfccc_submission_2015}. The largest contribution to global \gls{GHG} emissions, some 73\%, comes from energy consumption in the transportation, electricity and heat, buildings, manufacturing, and construction sectors \cite{ge_4_2020}. However, there is significant uncertainty surrounding these carbon-neutral energy transitions regarding the economically optimal shares and deployment rates of clean energy sources and their long-term impact on the energy system. The emergence of novel technologies like \gls{CCS} and hydrogen power also raises questions about their role in \gls{GHG} mitigation and the sensitivity of the energy transition to uncertainties in these technologies' investment cost, efficiency, and carbon footprint.

We are probing these questions by simulating cost-optimised energy transitions in the electricity supply sector with rigid carbon constraints using a suite of existing and emerging electricity generation and storage technologies. We use Japan as a proxy for a developed nation committed to addressing climate change. However, the results have global significance. Like many other developed nations, Japan has been rapidly deploying renewables and has attempted to transition away from nuclear power since the Fukushima Daiichi accident \cite{international_energy_agency_latest_2019}. Yet Japan is also considering reinvigorating its nuclear power sector, evidenced by the restart of its nuclear reactors \cite{iaea_pris_nodate}. Additionally, Japan is actively developing plans to deploy hydrogen power under the Basic Hydrogen Strategy \cite{meti_basic_2017} and has shown interest in utilising \gls{CCS} \cite{meti_report_2020}. Therefore, due to Japan's similarity to other developed nations and its willingness to consider a variety of commercial and pre-commercial low-carbon technologies, lessons learnt from these decarbonisation simulations could inform global energy policy by delineating potential transition pathways, identifying key novel technologies, and their most significant parameters.

%Developed nations rich in natural resources can reduce \gls{GHG} emissions by switching to natural gas or implementing \gls{CCS} at fossil fuel plants. However, these options are often economically infeasible for developing nations, which will lead to increased emissions through greater coal use \cite{international_energy_agency_latest_2019}. Japan, a developed nation without fossil fuel resources, is likely to follow a different path to reduce emissions, evidenced by the restart of nuclear reactors and a shift towards large-scale renewable energy deployment .

The context of the Japanese transition strategy also captures the priorities, subtle limitations, and lack of specificity in other developed nations' energy transition plans. Although influenced by the Paris Agreements, Japanese energy policy is governed chiefly by the Basic Energy Plan \cite{meti_japans_2018}, which outlines national policy towards a new energy system for the years 2030 and 2050 cognizant of limited indigenous resources, the impact of the Fukushima incident, and external pressures on energy supplies \cite{meti_annual_2018}. The plan reaffirms Japanese benchmarks for evaluating the energy system, first and foremost, within the context of energy security, followed by economic efficiency, safety, and the environment (summarised as `3E+S'; ibid). Although the Japanese 3E+S goals and the Paris Agreement targets have some parallels, the plan does not detail how the 2050 emission reduction target of 80\% is to be met. Matsuo et. al have suggested that electrification of a number of sectors will be required to achieve the ambitious 2050 target, underpinned by low-carbon technologies \cite{matsuo_quantitative_2018}. For the power sector to achieve such a target, near-zero emissions are required, and early action utilising existing technologies is preferable to delayed action utilising future technologies \cite{ashina_roadmap_2012}. The strategies currently under consideration include reinvigorating nuclear power, deploying \gls{CCS} to fossil fuel power plants, and ushering in a hydrogen economy based on renewable energy-based electrolysis as well as hydrogen imports from abroad \cite{ashina_roadmap_2012, matsuo_quantitative_2018, meti_basic_2017}.
